
### load data and remove outliers
```{r}
library(tidyverse)
library('corrr')
library(ggcorrplot)
library(car)

core_post = '_eighty' # ['_eighty', ''] # different core developer identification approach
month_period = '24' # different length of interaction period
data_novelty = read_csv('./data/repo_property_novelty_com_Python_before_2022_vd_256.csv')
data_network_commit = read_csv(sprintf('./data/network_stats_com_Python_before_2022_month_%s_act_commit%s.csv', month_period, core_post))
data_network_issue = read_csv(sprintf('./data/network_stats_com_Python_before_2022_month_%s_act_issue%s.csv', month_period, core_post))
data_network_star = read_csv(sprintf('./data/network_stats_com_Python_before_2022_month_%s_act_star%s.csv', month_period, core_post))
data_meta = read_csv(sprintf('./data/repo_meta_com_Python_before_2022%s.csv', core_post))
data_validation = read_csv('./data/repo_validate_novelty_b_10.csv')


df_project_m = merge(data_novelty, data_network_commit, by = 'repo_slug')
df_project_m = merge(df_project_m, data_network_issue, by = 'repo_slug')
df_project_m = merge(df_project_m, data_network_star, by = 'repo_slug')
df_project_m = merge(df_project_m, data_validation, by = 'repo_slug')

df_project_m = merge(df_project_m, data_meta, by = 'repo_slug')

df_project_m = subset(df_project_m, earliest_commit_year >= 2008 & pk_sim_mean > -999 & earliest_commit_year < 2021 & pk_sim_mean_valid > -999)

df_project_m$atypicality = -df_project_m$pk_sim_mean 
df_project_m$atypicality_validation = - df_project_m$pk_sim_mean_valid


hist(df_project_m$pk_sim_mean)
hist(log(df_project_m$owner_star_count_before + 1))
hist(log(df_project_m$outdegree_commit + 1))
hist(log(df_project_m$outdegree_issue + 1))
hist(log(df_project_m$outdegree_star + 1))
hist(log(df_project_m$package_count + 1))
hist(df_project_m$core_dev_count)
hist(log(df_project_m$core_dev_count+1))

t = subset(df_project_m, diversity_commit > -999 & 
                                              diversity_issue > -999 & 
                                              diversity_star > -999)
hist(t$diversity_commit)
hist(t$diversity_issue)
hist(t$diversity_star)


if ((core_post == '') && (month_period == '12')){
  df_project_m_no_outlier = subset(df_project_m, pk_sim_mean > -0.2 & pk_sim_mean < 0.7 
                                                & owner_star_count_before < exp(7)
                                                & outdegree_commit < exp(4)
                                                & outdegree_issue < exp(3)
                                                & outdegree_star < exp(5)
                                                & package_count < exp(3.5)
                                                & core_dev_count < 6 & core_dev_count > 0
                                                & diversity_commit < -0.3 
                                                & diversity_issue < -0.15
                                                & diversity_star < -0.1)
  
  

}else if((core_post == '') && (month_period == '6')){
  df_project_m_no_outlier = subset(df_project_m, pk_sim_mean > -0.2 & pk_sim_mean < 0.7 
                                                & owner_star_count_before < exp(7)
                                                & outdegree_commit < exp(3.5)
                                                & outdegree_issue < exp(2)
                                                & outdegree_star < exp(4)
                                                & package_count < exp(3.5)
                                                & core_dev_count < 6 & core_dev_count > 0
                                                & diversity_commit < -0.3 
                                                & diversity_issue < -0.15
                                                & diversity_star < -0.1)
  
  
}else if((core_post == '') && (month_period == '24')){
  df_project_m_no_outlier = subset(df_project_m, pk_sim_mean > -0.2 & pk_sim_mean < 0.7 
                                                & owner_star_count_before < exp(7)
                                                & outdegree_commit < exp(4)
                                                & outdegree_issue < exp(3)
                                                & outdegree_star < exp(5)
                                                & package_count < exp(4)
                                                & core_dev_count < 6 & core_dev_count > 0
                                                & diversity_commit < -0.25 
                                                & diversity_issue < -0.1
                                                & diversity_star < -0.1)
  
  
}else if((core_post == '_eighty') && (month_period == '6')){
  df_project_m_no_outlier = subset(df_project_m, pk_sim_mean > -0.2 & pk_sim_mean < 0.7 
                                                & owner_star_count_before < exp(7)
                                                & outdegree_commit < exp(4)
                                                & outdegree_issue < exp(2.5)
                                                & outdegree_star < exp(4)
                                                & package_count < exp(4)
                                                & core_dev_count < exp(2) & core_dev_count > 0
                                                & diversity_commit < -0.25
                                                & diversity_issue < -0.15
                                                & diversity_star < -0.05)
  
  
}else if((core_post == '_eighty') && (month_period == '12')){
  df_project_m_no_outlier = subset(df_project_m, pk_sim_mean > -0.2 & pk_sim_mean < 0.7 
                                                & owner_star_count_before < exp(7)
                                                & outdegree_commit < exp(4)
                                                & outdegree_issue < exp(3)
                                                & outdegree_star < exp(5)
                                                & package_count < exp(4)
                                                & core_dev_count < exp(2) & core_dev_count > 0
                                                & diversity_commit < -0.2
                                                & diversity_issue < -0.1
                                                & diversity_star < -0.05)
  
  
}else if((core_post == '_eighty') && (month_period == '24')){
  df_project_m_no_outlier = subset(df_project_m, pk_sim_mean > -0.2 & pk_sim_mean < 0.7 
                                                & owner_star_count_before < exp(7)
                                                & outdegree_commit < exp(5)
                                                & outdegree_issue < exp(3.5)
                                                & outdegree_star < exp(5)
                                                & package_count < exp(4)
                                                & core_dev_count < exp(2) & core_dev_count > 0
                                                & diversity_commit < -0.2
                                                & diversity_issue < -0.1
                                                & diversity_star < -0.05)
  
  
}
df_project_m_diversity_no_outlier = subset(df_project_m_no_outlier, diversity_commit > -999 & 
                                              diversity_issue > -999 & 
                                              diversity_star > -999)
# Fang's metric for validation

rm(data_novelty)
rm(data_network_commit)
rm(data_network_issue)
rm(data_network_star)
rm(data_meta)

rm(df_project_m)


```

### PCA construction for average and weak degrees, complete sample
```{r}

df_project_m_no_outlier$scaled_log_degree_colab_out = scale(log(df_project_m_no_outlier$outdegree_commit + 1))
df_project_m_no_outlier$scaled_log_degree_issue_out = scale(log(df_project_m_no_outlier$outdegree_issue + 1))
df_project_m_no_outlier$scaled_log_degree_star_out = scale(log(df_project_m_no_outlier$outdegree_star + 1))




variable_out_degree = df_project_m_no_outlier[, c('scaled_log_degree_colab_out', 'scaled_log_degree_issue_out',  'scaled_log_degree_star_out')]


pca_out_degree = prcomp(variable_out_degree)

princomp(variable_out_degree)

summary(pca_out_degree)

pca_out_degree$rotation

if (pca_out_degree$rotation["scaled_log_degree_star_out", 1] < 0) {
  stopifnot(pca_out_degree$rotation["scaled_log_degree_issue_out", 1] < 0)
  stopifnot(pca_out_degree$rotation["scaled_log_degree_colab_out", 1] < 0)

  df_project_m_no_outlier$ave_degree_out = -pca_out_degree$x[, 1]

} else {
  stopifnot(pca_out_degree$rotation["scaled_log_degree_issue_out", 1] > 0)
  stopifnot(pca_out_degree$rotation["scaled_log_degree_colab_out", 1] > 0)

  df_project_m_no_outlier$ave_degree_out = pca_out_degree$x[, 1]
}

if (pca_out_degree$rotation["scaled_log_degree_star_out", 2] < 0) {
  stopifnot(pca_out_degree$rotation["scaled_log_degree_star_out", 2] < pca_out_degree$rotation["scaled_log_degree_issue_out", 2])
  stopifnot(pca_out_degree$rotation["scaled_log_degree_issue_out", 2] < pca_out_degree$rotation["scaled_log_degree_colab_out", 2])

  df_project_m_no_outlier$weakness_out = -pca_out_degree$x[, 2]

} else {
  stopifnot(pca_out_degree$rotation["scaled_log_degree_star_out", 2] > pca_out_degree$rotation["scaled_log_degree_issue_out", 2])
  stopifnot(pca_out_degree$rotation["scaled_log_degree_issue_out", 2] > pca_out_degree$rotation["scaled_log_degree_colab_out", 2])

  df_project_m_no_outlier$weakness_out = pca_out_degree$x[, 2]
}

```

### PCA construction for average and weak degrees, for samples with valid diversity metric

```{r}



df_project_m_diversity_no_outlier$scaled_log_degree_colab_out = scale(log(df_project_m_diversity_no_outlier$outdegree_commit + 1))

df_project_m_diversity_no_outlier$scaled_log_degree_issue_out = scale(log(df_project_m_diversity_no_outlier$outdegree_issue + 1))


df_project_m_diversity_no_outlier$scaled_log_degree_star_out = scale(log(df_project_m_diversity_no_outlier$outdegree_star + 1))




variable_out_degree = df_project_m_diversity_no_outlier[, c('scaled_log_degree_colab_out', 'scaled_log_degree_issue_out', 'scaled_log_degree_star_out')]

pca_out_degree = prcomp(variable_out_degree)

princomp(variable_out_degree)

summary(pca_out_degree)

pca_out_degree$rotation

if (pca_out_degree$rotation["scaled_log_degree_star_out", 1] < 0) {
  stopifnot(pca_out_degree$rotation["scaled_log_degree_issue_out", 1] < 0)
  stopifnot(pca_out_degree$rotation["scaled_log_degree_colab_out", 1] < 0)

  df_project_m_diversity_no_outlier$ave_degree_out = -pca_out_degree$x[, 1]

} else {
  stopifnot(pca_out_degree$rotation["scaled_log_degree_issue_out", 1] > 0)
  stopifnot(pca_out_degree$rotation["scaled_log_degree_colab_out", 1] > 0)

  df_project_m_diversity_no_outlier$ave_degree_out = pca_out_degree$x[, 1]
}


if (pca_out_degree$rotation["scaled_log_degree_star_out", 2] < 0) {
  stopifnot(pca_out_degree$rotation["scaled_log_degree_star_out", 2] < pca_out_degree$rotation["scaled_log_degree_issue_out", 2])
  stopifnot(pca_out_degree$rotation["scaled_log_degree_issue_out", 2] < pca_out_degree$rotation["scaled_log_degree_colab_out", 2])

  df_project_m_diversity_no_outlier$weakness_out = -pca_out_degree$x[, 2]
} else {
  stopifnot(pca_out_degree$rotation["scaled_log_degree_star_out", 2] > pca_out_degree$rotation["scaled_log_degree_issue_out", 2])
  stopifnot(pca_out_degree$rotation["scaled_log_degree_issue_out", 2] > pca_out_degree$rotation["scaled_log_degree_colab_out", 2])

  df_project_m_diversity_no_outlier$weakness_out = pca_out_degree$x[, 2]
}



```








### PCA construction for average and weak diversity, for samples with valid diversity metric

```{r}




df_project_m_diversity_no_outlier$scaled_diversity_commit = scale(df_project_m_diversity_no_outlier$diversity_commit)
df_project_m_diversity_no_outlier$scaled_diversity_issue = scale(df_project_m_diversity_no_outlier$diversity_issue)

df_project_m_diversity_no_outlier$scaled_diversity_star = scale(df_project_m_diversity_no_outlier$diversity_star)



variable_out_diversity = df_project_m_diversity_no_outlier[, c('scaled_diversity_commit', 'scaled_diversity_issue', 'scaled_diversity_star')]
pca_out_diversity = prcomp(variable_out_diversity)

princomp(variable_out_diversity)

summary(pca_out_diversity)

pca_out_diversity$rotation


if (pca_out_diversity$rotation["scaled_diversity_star", 1] < 0) {
  stopifnot(pca_out_diversity$rotation["scaled_diversity_issue", 1] < 0)
  stopifnot(pca_out_diversity$rotation["scaled_diversity_commit", 1] < 0)

  df_project_m_diversity_no_outlier$ave_diversity_out = -pca_out_diversity$x[, 1]
} else {
  stopifnot(pca_out_diversity$rotation["scaled_diversity_issue", 1] > 0)
  stopifnot(pca_out_diversity$rotation["scaled_diversity_commit", 1] > 0)
  df_project_m_diversity_no_outlier$ave_diversity_out = pca_out_diversity$x[, 1]
}


if (pca_out_diversity$rotation["scaled_diversity_star", 2] < 0) {
  stopifnot(pca_out_diversity$rotation["scaled_diversity_star", 2] < pca_out_diversity$rotation["scaled_diversity_issue", 2])
  stopifnot(pca_out_diversity$rotation["scaled_diversity_issue", 2] < pca_out_diversity$rotation["scaled_diversity_commit", 2])

  df_project_m_diversity_no_outlier$weakness_diversity = -pca_out_diversity$x[, 2]
} else {
  stopifnot(pca_out_diversity$rotation["scaled_diversity_star", 2] > pca_out_diversity$rotation["scaled_diversity_issue", 2])
  stopifnot(pca_out_diversity$rotation["scaled_diversity_issue", 2] > pca_out_diversity$rotation["scaled_diversity_commit", 2])

  df_project_m_diversity_no_outlier$weakness_diversity = pca_out_diversity$x[, 2]
}





```


### Generate Table 3, 6, 7, 8 using atypicality as outcome, or generate Table 5 using atypicality_validation as outcome
```{r}
# change the outcome variable to atypicality_validation for Fang's metric (for validation purpose)
m_degree_all_model = lm(atypicality~
                                  ave_degree_out +
                                  weakness_out +
                                  owner_org +
                                  log(owner_star_count_before + 1) +
                                  log(core_dev_count) +
                                  log(package_count) +
                                   as.factor(earliest_commit_year)
                                  ,data = df_project_m_no_outlier)
vif(m_degree_all_model)
summary(m_degree_all_model)


m_degree_dv_model = lm(atypicality~
                                  ave_degree_out +
                                  weakness_out +
                                  owner_org +
                                  log(owner_star_count_before + 1) +
                                  log(core_dev_count) +
                                  log(package_count) +
                                   as.factor(earliest_commit_year)
                                  ,data = df_project_m_diversity_no_outlier)
vif(m_degree_dv_model)
summary(m_degree_dv_model)




m_diversity_dv_model = lm(atypicality~
                                  ave_diversity_out +
                                  weakness_diversity +
                                  owner_org +
                                  log(owner_star_count_before + 1) +
                                  log(core_dev_count) +
                                  log(package_count) +
                                   as.factor(earliest_commit_year)
                                  ,data = df_project_m_diversity_no_outlier)
vif(m_diversity_dv_model)
summary(m_diversity_dv_model)

m_diversity_degree_dv_model = lm(atypicality~
                                  ave_degree_out +
                                  weakness_out +
                                  ave_diversity_out +
                                  weakness_diversity +
                                  owner_org +
                                  log(owner_star_count_before + 1) +
                                  log(core_dev_count) +
                                  log(package_count) +
                                   as.factor(earliest_commit_year)
                                  ,data = df_project_m_diversity_no_outlier)
vif(m_diversity_degree_dv_model)
summary(m_diversity_degree_dv_model)





```


### generate temp data to replicate Figure 2.a


```{r}
# Load necessary libraries
library(dplyr)
library(broom)
# Initialize an empty dataframe to store results
results_df <- data.frame(year = integer(), ave_diversity_out.coef = numeric(), ave_diversity_out.lower_ci = numeric(), ave_diversity_out.upper_ci = numeric(), weakness_diversity.coef = numeric(), weakness_diversity.lower_ci = numeric(), weakness_diversity.upper_ci = numeric())

# Loop over each year from 2008 to 2020
for (year in 2008:2020) {
  # Subset data for the current year
  df_subset <- subset(df_project_m_diversity_no_outlier, earliest_commit_year == year)
  
  # Run the linear regression model
  model <- lm(atypicality~   ave_diversity_out +
                                  weakness_diversity +
                                  log(package_count) +
                                  owner_org +
                                  log(owner_star_count_before + 1) +
                                  log(core_dev_count)
                                  ,data = df_subset)
  
  # Extract coefficients and confidence intervals for ave_degree_out and weakness_out
  tidy_results <- tidy(model)
  coef_ave_degree_out <- tidy_results[tidy_results$term == "ave_diversity_out", "estimate"]
  ci_ave_degree_out <- confint(model, "ave_diversity_out")
  coef_weakness_out <- tidy_results[tidy_results$term == "weakness_diversity", "estimate"]
  ci_weakness_out <- confint(model, "weakness_diversity")
  
  # Append results to the dataframe
  results_df <- rbind(results_df, data.frame(year = year, ave_diversity_out.coef = coef_ave_degree_out, ave_diversity_out.lower_ci = ci_ave_degree_out[1], ave_diversity_out.upper_ci = ci_ave_degree_out[2], weakness_diversity.coef = coef_weakness_out, weakness_diversity.lower_ci = ci_weakness_out[1], weakness_diversity.upper_ci = ci_weakness_out[2]))
}


colnames(results_df)[colnames(results_df) == "estimate"] <- "ave_diversity_out.coef"
colnames(results_df)[colnames(results_df) == "estimate.1"] <- "weakness_diversity.coef"


# Save results to a CSV file
write.csv(results_df, "./temp_data/results_diversity_div_sample_yearly_cohort.csv", row.names = FALSE)


```


### visualize figure 2.a
```{r}

# Load required libraries
library(ggplot2)
library(tidyr)
library(reshape2)
# Read the CSV file
year_cut_off = 2010

data <- read.csv("./temp_data/results_diversity_div_sample_yearly_cohort.csv")

# Convert the data to long format for plotting
df_long <- melt(data, id.vars = "year", variable.name = "variable_name")

# Split the variable_name column into coef, lower_ci, and upper_ci
df_long <- cbind(df_long, colsplit(df_long$variable_name, "\\.", c("variable", "stat")))

# Drop the original variable_name column
df_long <- df_long[, -which(names(df_long) == "variable_name")]


# Rename columns
colnames(df_long) <- c("year", "value", "Varible", "category")

df_wide <- spread(df_long, key = category, value = value)
df_wide = subset(df_wide, year > year_cut_off)

df_wide[df_wide$Varible == "ave_diversity_out", "year"] <- df_wide[df_wide$Varible == "ave_diversity_out", "year"] - 0.1
df_wide[df_wide$Varible == "ave_degree_out", "year"] <- df_wide[df_wide$Varible == "ave_degree_out", "year"] - 0.1

df_wide[df_wide == 'ave_degree_out'] = 'Average Degree'
df_wide[df_wide == 'ave_diversity_out'] = 'Average Diversity'
df_wide[df_wide == 'weakness_out'] = 'Degree from Weak Tie'
df_wide[df_wide == 'weakness_diversity'] = 'Diversity from Weak Tie'


linewidth = 2
x_ticks <- seq(year_cut_off + 1, 2020, by = 1)

# Plot the data
ggplot(df_wide, aes(x = year, y = coef, color = Varible)) +
  geom_line(size = linewidth) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.5, size = linewidth) +
  labs(title = "",
       x = "Year",
       y = "Estimated Coefficient",
       color = "Variables") +
    geom_hline(yintercept=0, linetype = 'dashed', color = 'gray', size = linewidth) +
  scale_color_manual(values = c("Average Degree" = "blue", "Average Diversity" = "blue", "Diversity from Weak Tie" = "red", "Degree from Weak Tie" = "red")) +
  scale_x_continuous(breaks = x_ticks)+
  theme_classic()+
  theme(legend.text = element_text(size=26),
        axis.text.x =element_text(size=28),
        axis.text.y =element_text(size=28),
        axis.title.x=element_text(size=28),
        axis.title.y=element_text(size=28),
        legend.title=element_text(size=28))

ggsave(file="./figure/diversity_div_yearly.pdf", width=20, height=9, dpi=300)


```


### generate temp data to replicate Figure 2.b
```{r}
# Load necessary libraries
library(dplyr)
library(broom)
# Initialize an empty dataframe to store results
results_df <- data.frame(core_dev_count = integer(), ave_diversity_out.coef = numeric(), ave_diversity_out.lower_ci = numeric(), ave_diversity_out.upper_ci = numeric(), weakness_diversity.coef = numeric(), weakness_diversity.lower_ci = numeric(), weakness_diversity.upper_ci = numeric())

t1 <- subset(df_project_m_diversity_no_outlier, core_dev_count == 1)
summary(t1$ave_diversity_out)

t2 <- subset(df_project_m_diversity_no_outlier, core_dev_count == 2)
summary(t2$ave_diversity_out)

t3 <- subset(df_project_m_diversity_no_outlier, core_dev_count == 3)
summary(t3$ave_diversity_out)

t4 <- subset(df_project_m_diversity_no_outlier, core_dev_count == 4)
summary(t4$ave_diversity_out)

t5 <- subset(df_project_m_diversity_no_outlier, core_dev_count == 5)
summary(t5$ave_diversity_out)


for (core_dev_count_target in 1:5) {
  # Subset data for the current year
  df_subset <- subset(df_project_m_diversity_no_outlier, core_dev_count == core_dev_count_target)
  
  # Run the linear regression model
  model <- lm(atypicality~   ave_diversity_out +
                                  weakness_diversity +
                                  log(package_count) +
                                  owner_org +
                                  log(owner_star_count_before + 1) +
                                  as.factor(earliest_commit_year)
                                  ,data = df_subset)
  
  # Extract coefficients and confidence intervals for ave_degree_out and weakness_out
  tidy_results <- tidy(model)
  coef_ave_degree_out <- tidy_results[tidy_results$term == "ave_diversity_out", "estimate"]
  ci_ave_degree_out <- confint(model, "ave_diversity_out")
  coef_weakness_out <- tidy_results[tidy_results$term == "weakness_diversity", "estimate"]
  ci_weakness_out <- confint(model, "weakness_diversity")
  
  # Append results to the dataframe
  results_df <- rbind(results_df, data.frame(core_dev_count = core_dev_count_target, ave_diversity_out.coef = coef_ave_degree_out, ave_diversity_out.lower_ci = ci_ave_degree_out[1], ave_diversity_out.upper_ci = ci_ave_degree_out[2], weakness_diversity.coef = coef_weakness_out, weakness_diversity.lower_ci = ci_weakness_out[1], weakness_diversity.upper_ci = ci_weakness_out[2]))
}


colnames(results_df)[colnames(results_df) == "estimate"] <- "ave_diversity_out.coef"
colnames(results_df)[colnames(results_df) == "estimate.1"] <- "weakness_diversity.coef"


# Save results to a CSV file
write.csv(results_df, "./temp_data/results_diversity_div_sample_core_cohort.csv", row.names = FALSE)


```



### visualize figure 2.b
```{r}

# Load required libraries
library(ggplot2)
library(tidyr)
library(reshape2)
# Read the CSV file
data <- read.csv("./temp_data/results_diversity_div_sample_core_cohort.csv")

# Convert the data to long format for plotting
df_long <- melt(data, id.vars = "core_dev_count", variable.name = "variable_name")

# Split the variable_name column into coef, lower_ci, and upper_ci
df_long <- cbind(df_long, colsplit(df_long$variable_name, "\\.", c("variable", "stat")))

# Drop the original variable_name column
df_long <- df_long[, -which(names(df_long) == "variable_name")]


# Rename columns
colnames(df_long) <- c("core_dev_count", "value", "Varible", "category")

df_wide <- spread(df_long, key = category, value = value)

df_wide[df_wide$Varible == "ave_diversity_out", "core_dev_count"] <- df_wide[df_wide$Varible == "ave_diversity_out", "core_dev_count"] - 0.1
df_wide[df_wide$Varible == "ave_degree_out", "core_dev_count"] <- df_wide[df_wide$Varible == "ave_degree_out", "core_dev_count"] - 0.1

df_wide[df_wide == 'ave_degree_out'] = 'Average Degree'
df_wide[df_wide == 'ave_diversity_out'] = 'Average Diversity'
df_wide[df_wide == 'weakness_out'] = 'Degree from Weak Tie'
df_wide[df_wide == 'weakness_diversity'] = 'Diversity from Weak Tie'


linewidth = 2
x_ticks <- seq(1, 5, by = 1)

# Plot the data
ggplot(df_wide, aes(x = core_dev_count, y = coef, color = Varible)) +
  geom_line(size = linewidth) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.5, size = linewidth) +
  labs(title = "",
       x = "Core Developer Count",
       y = "Estimated Coefficient",
       color = "Variables") +
    geom_hline(yintercept=0, linetype = 'dashed', color = 'gray', size = linewidth) +
  scale_color_manual(values = c("Average Degree" = "blue", "Average Diversity" = "blue", "Diversity from Weak Tie" = "red", "Degree from Weak Tie" = "red")) +
  scale_x_continuous(breaks = x_ticks)+
  theme_classic()+
  theme(legend.text = element_text(size=26),
        axis.text.x =element_text(size=28),
        axis.text.y =element_text(size=28),
        axis.title.x=element_text(size=28),
        axis.title.y=element_text(size=28),
        legend.title=element_text(size=28))



ggsave(file="./figure/diversity_div_sample_core_cohort.pdf", width=20, height=9, dpi=300)


```



### generate temp data to replicate Figure 2.c

```{r}
library(dplyr)
library(broom)
df_project_m_diversity_org = subset(df_project_m_diversity_no_outlier, owner_org == TRUE)
df_project_m_diversity_ind = subset(df_project_m_diversity_no_outlier, owner_org == FALSE)

m_div_dv_model_org = lm(atypicality~

                                  ave_diversity_out +
                                  weakness_diversity +
                                  log(owner_star_count_before + 1) +
                                  log(core_dev_count) +
                                  log(package_count) +

                                   as.factor(earliest_commit_year)
                                  ,data = df_project_m_diversity_org)


m_div_dv_model_ind = lm(atypicality~

                                  ave_diversity_out +
                                  weakness_diversity +
                                  log(owner_star_count_before + 1) +
                                  log(core_dev_count) +
                                  log(package_count) +

                                   as.factor(earliest_commit_year)
                                  ,data = df_project_m_diversity_ind)



### diversity


results_df <- data.frame(category = integer(), ave_degree_out.coef = numeric(), ave_degree_out.lower_ci = numeric(), ave_degree_out.upper_ci = numeric(), weakness_out.coef = numeric(), weakness_out.lower_ci = numeric(), weakness_out.upper_ci = numeric())
# 0 for org, 1 for ind
for (model_cat_pair in list(list(m_div_dv_model_org, 0), list(m_div_dv_model_ind, 1))){
model = model_cat_pair[[1]]
cat = model_cat_pair[[2]]

tidy_results <- tidy(model)
coef_ave_degree_out <- tidy_results[tidy_results$term == "ave_diversity_out", "estimate"]
ci_ave_degree_out <- confint(model, "ave_diversity_out")
coef_weakness_out <- tidy_results[tidy_results$term == "weakness_diversity", "estimate"]
ci_weakness_out <- confint(model, "weakness_diversity")

# Append results to the dataframe
results_df <- rbind(results_df, data.frame(category = cat, ave_diversity_out.coef = coef_ave_degree_out, ave_diversity_out.lower_ci = ci_ave_degree_out[1], ave_diversity_out.upper_ci = ci_ave_degree_out[2], weakness_diversity.coef = coef_weakness_out, weakness_diversity.lower_ci = ci_weakness_out[1], weakness_diversity.upper_ci = ci_weakness_out[2]))
}


colnames(results_df)[colnames(results_df) == "estimate"] <- "ave_diversity_out.coef"
colnames(results_df)[colnames(results_df) == "estimate.1"] <- "weakness_diversity.coef"


write.csv(results_df, "./temp_data/results_div_org_cohort.csv", row.names = FALSE)

```










### visualize figure 2.c
```{r}

# Load required libraries
library(ggplot2)
library(tidyr)
library(reshape2)
# Read the CSV file
data <- read.csv("./temp_data/results_div_org_cohort.csv")

# Convert the data to long format for plotting
df_long <- melt(data, id.vars = "category", variable.name = "variable_name")

# Split the variable_name column into coef, lower_ci, and upper_ci
df_long <- cbind(df_long, colsplit(df_long$variable_name, "\\.", c("variable", "stat")))

# Drop the original variable_name column
df_long <- df_long[, -which(names(df_long) == "variable_name")]


# Rename columns
colnames(df_long) <- c("owner_type", "value", "Varible", "category")

df_wide <- spread(df_long, key = category, value = value)

df_wide[df_wide$Varible == "ave_diversity_out", "owner_type"] <- df_wide[df_wide$Varible == "ave_diversity_out", "owner_type"] - 0.1
df_wide[df_wide$Varible == "ave_degree_out", "owner_type"] <- df_wide[df_wide$Varible == "ave_degree_out", "owner_type"] - 0.1

df_wide[df_wide == 'ave_degree_out'] = 'Average Degree'
df_wide[df_wide == 'ave_diversity_out'] = 'Average Diversity'
df_wide[df_wide == 'weakness_out'] = 'Degree from Weak Tie'
df_wide[df_wide == 'weakness_diversity'] = 'Diversity from Weak Tie'


linewidth = 2
x_ticks <- seq(0, 1, by = 1)
# df_wide$owner_type = as.factor(df_wide$owner_type)
# Plot the data
ggplot(df_wide, aes(x = owner_type, y = coef, color = Varible)) +
  # geom_line(size = linewidth) +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), width = 0.5, size = linewidth) +
  labs(title = "",
       x = "Owner Identity",
       y = "Estimated Coefficient",
       color = "Variables") +
    geom_hline(yintercept=0, linetype = 'dashed', color = 'gray', size = linewidth) +
  scale_color_manual(values = c("Average Degree" = "blue", "Average Diversity" = "blue", "Diversity from Weak Tie" = "red", "Degree from Weak Tie" = "red")) +
  scale_x_continuous(breaks = x_ticks, labels= c('Org', 'Ind'))+
  theme_classic()+
  theme(legend.text = element_text(size=26),
        axis.text.x =element_text(size=28),
        axis.text.y =element_text(size=28),
        axis.title.x=element_text(size=28),
        axis.title.y=element_text(size=28),
        legend.title=element_text(size=28))


ggsave(file="./figure/diversity_div_sample_org_cohort.pdf", width=20, height=9, dpi=300)



```




### visualize figure 4, load
```{r}

data_validation_awesome_list = read_csv('./data/repo_property_novelty_awesome_list.csv')
df_project_m_diversity_no_outlier = merge(df_project_m_diversity_no_outlier, data_validation_awesome_list, by = 'repo_slug')

```

### generate Figure 4 and Table 9
```{r}


t_m = lm(atypicality ~
                        is_awesome + 
                        owner_org +
                        log(owner_star_count_before + 1) +
                        log(core_dev_count) +
                        log(package_count) +
                         as.factor(earliest_commit_year)
                      ,data= df_project_m_diversity_no_outlier)
summary(t_m)
awesome_project = subset(df_project_m_diversity_no_outlier, is_awesome == TRUE)
no_awesome_project = subset(df_project_m_diversity_no_outlier, is_awesome == FALSE)
t.test(awesome_project$atypicality, no_awesome_project$atypicality) # t-test


ggplot(df_project_m_diversity_no_outlier, aes(x = as.factor(is_awesome), y = atypicality)) +
  geom_violin() +
  labs(x = "Whether awesome projects", y = "Atypicality") +
  # scale_fill_manual(values = c("FALSE" = "blue", "TRUE" = "red")) +
  theme_minimal() + 
  theme(panel.grid = element_blank(),
        axis.line = element_line(color = "black"),  # Adds x and y axis lines
            axis.title.x = element_text(size = 26),  # Adjust the size of the x-axis title
    axis.title.y = element_text(size = 26),  # Adjust the size of the y-axis title
    axis.text.x = element_text(size = 22),   # Adjust the size of the x-axis text
    axis.text.y = element_text(size = 22)    # Adjust the size of the y-axis text
            ) +
  geom_hline(data = df_project_m_diversity_no_outlier %>%
               group_by(is_awesome) %>%
               summarise(mean_atypicality = mean(atypicality)),
             aes(yintercept = mean_atypicality), linetype = "22", color = "gray", linewidth = 2) +
stat_summary(fun.y=mean, geom="point", size=4, color="red")

ggsave("./figure/awesome_atypicality.pdf", device = "pdf", width = 7, height = 5)

```
